### 2019-03-19 papers/journal/encoding.tex
exmaple update

Our first attempt was to encode the existential condition check as a $\fbmc$ search problem~\cite{plospaper}.
%
%In this section we will present the $\fbmc$ encoding of the same.
%
Although the techniques used for $\fbmc$ and $\fsmt$ is very different because we are not unrolling the complete program in the case of $\fbmc$, the encoding is not considerably different.
% 
The $\fbmc$ search encoding differs with the presented $\fsmt$ encoding in the way variables are represented and how we encode reachability (both for the stability and connectivity).  
%
Here, we will only present the stability encoding.
%the rest of the encodings are similar to the one presented in the previous section, Section~\ref{enc:smt}.

@@

The following constraints encode the basic consistency of VTSs. 
%
Recall that now the molecule set is divided into 3:1 Q and R pairs (or partition).
\begin{align*}
\texttt{EdgeC} =\;&\hspace{-1ex}\bigwedge\limits_{i,j,q} (\bigvee_m e_{i,j,q,m} )\limplies e_{i,j,q}
\land
\bigwedge\limits_{i,q} \neg e_{i,i,q}
\land
% \tag{\texttt{NodeC}}\label{eq:f0}\\
\bigwedge\limits_{\mathclap{i,j,q,m}} e_{i,j,q,m} \limplies (n_{i,m} \land n_{j,m} )
\\
\texttt{ActivityC} =\;&
\bigwedge\limits_{\mathclap{i,j,q,m}} b_{i,j,q,m} \limplies e_{i,j,q,m} \quad\land\quad
\bigwedge\limits_{i,m} a_{i,m} \limplies n_{i,m}
% \tag{V2}\label{eq:f1}\\
\\
\texttt{PairingC} =\;&
\exists qr. \Land\limits_{\mathrlap{m_1,m_2,m_3,m_4}\;\;}
(p_{\{m_1,m_2,m_3,m_4\}} \limplies qr_{m_1} + qr_{m_2} + qr_{m_3} + qr_{m_4} = 3) 
% \land\\ 
%   & \quad\quad\quad ( m_1 = m_2 = m_3 = m_4  \limplies \lnot p_{m_1,m_2,m_3,m_4} )
% \bigwedge\limits_{m} 
% (\Lor\limits_{m'} p_{mm'} \limplies \Land_{m'} \lnot p_{m'm} ) \land
% (\Lor\limits_{m'} p_{m'm} \limplies \Land_{m'} \lnot p_{mm'} )
\\
\texttt{Fusion1} =\;&
\bigwedge\limits_{i,j,q} e_{i,j,q} \limplies
\bigvee_{{m_1,m_2,m_3,m_4}} (\Land_{l=1}^4 ( b_{i,j,q,m_l} \lor a_{j,m_l} ) \land 
\Lor\limits_{l=1}^4 b_{i,j,q,m_l} \land\\
& \qquad \qquad \qquad \qquad \Lor\limits_{l=1}^4 a_{j,m_l}\land p_{\{m_1,m_2,m_3,m_4\}})
\\
\texttt{Fusion2} =\;&
\bigwedge\limits_{\mathclap{i,j,q,m_1,m_2,m_3, l \in \{1,..,3\}}} b_{i,j,q,m_1} \land ..\land b_{i,j,q,m_l} \limplies \\
& \hspace{2cm} \neg 
\bigvee_{\mathclap{j \neq j^{\prime}, m_{l+1}^{\prime},..,m_{4}^{\prime}}} ( a_{j^{\prime},m_{l+1}^{\prime}} \land .. \land a_{j^{\prime},m_4^{\prime}} \land p_{\{m_1,..,m_l,m^{\prime}_{l+1},..,m^{\prime}_4\}})
\\
\texttt{Consistancy} =\;& \texttt{EdgeC} \land
\texttt{ActivityC} \land \texttt{PairingC} \land
\texttt{Fusion1} \land \texttt{Fusion2} 
\end{align*}
\texttt{EdgeC} states that each edge has at least one molecule,
there are no self loops, and edge labels are consistent with node labels.   
\texttt{ActivityC} states that active molecule are present.
\texttt{PairingC} states that all molecules are divided into two types
using $qr_m$ bit, which encodes if $m$ belongs to one type or another,
and any fusing set of molecules must have three molecules involved
from one type and one molecule from the other.
\texttt{Fusion1}, and \texttt{Fusion2} states the well-fused condition.
\texttt{Consistancy} is the conjunction of all of the above.

>>>>

Our first attempt was to encode the existential condition check as a $\fbmc$ search problem~\cite{shukla2017discovering}.
%
%In this section we will present the $\fbmc$ encoding of the same.
%
Although the techniques used for $\fbmc$ and $\fsmt$ is very different because we are not unrolling the complete program in the case of $\fbmc$, the encoding is not considerably different.
% 
The $\fbmc$ search encoding differs with the presented $\fsmt$ encoding in the way variables are represented and how we encode reachability (both for the stability and connectivity).  
%
Here, we will only present the stability encoding.
%the rest of the encodings are similar to the one presented in the previous section, Section~\ref{enc:smt}.

@@

The following constraints encode the basic consistency of VTSs. 
%
Recall that the molecule set is divided into 3:1 Q and R pairs (or partition).
\begin{align*}
\texttt{EdgeC} =\;&\hspace{-1ex}\bigwedge\limits_{i,j,q} (\bigvee_m e_{i,j,q,m} )\limplies e_{i,j,q}
\land
\bigwedge\limits_{i,q} \neg e_{i,i,q}
\land
% \tag{\texttt{NodeC}}\label{eq:f0}\\
\bigwedge\limits_{\mathclap{i,j,q,m}} e_{i,j,q,m} \limplies (n_{i,m} \land n_{j,m} )
\\
\texttt{ActivityC} =\;&
\bigwedge\limits_{\mathclap{i,j,q,m}} b_{i,j,q,m} \limplies e_{i,j,q,m} \quad\land\quad
\bigwedge\limits_{i,m} a_{i,m} \limplies n_{i,m}
% \tag{V2}\label{eq:f1}\\
\\
\texttt{PairingC} =\;&
\exists qr. \Land\limits_{\mathrlap{m_1,m_2,m_3,m_4}\;\;}
(p_{\{m_1,m_2,m_3,m_4\}} \limplies qr_{m_1} + qr_{m_2} + qr_{m_3} + qr_{m_4} = 3) 
% \land\\ 
%   & \quad\quad\quad ( m_1 = m_2 = m_3 = m_4  \limplies \lnot p_{m_1,m_2,m_3,m_4} )
% \bigwedge\limits_{m} 
% (\Lor\limits_{m'} p_{mm'} \limplies \Land_{m'} \lnot p_{m'm} ) \land
% (\Lor\limits_{m'} p_{m'm} \limplies \Land_{m'} \lnot p_{mm'} )
\\
\texttt{Fusion1} =\;&
\bigwedge\limits_{i,j,q} e_{i,j,q} \limplies
\bigvee_{{m_1,m_2,m_3,m_4}} (\Land_{l=1}^4 ( b_{i,j,q,m_l} \lor a_{j,m_l} ) \land 
\Lor\limits_{l=1}^4 b_{i,j,q,m_l} \land\\
& \qquad \qquad \qquad \qquad \Lor\limits_{l=1}^4 a_{j,m_l}\land p_{\{m_1,m_2,m_3,m_4\}})
\\
\texttt{Fusion2} =\;&
\bigwedge\limits_{\mathclap{i,j,q,m_1,m_2,m_3, l \in \{1,..,3\}}} b_{i,j,q,m_1} \land ..\land b_{i,j,q,m_l} \limplies \\
& \hspace{2cm} \neg 
\bigvee_{\mathclap{j \neq j^{\prime}, m_{l+1}^{\prime},..,m_{4}^{\prime}}} ( a_{j^{\prime},m_{l+1}^{\prime}} \land .. \land a_{j^{\prime},m_4^{\prime}} \land p_{\{m_1,..,m_l,m^{\prime}_{l+1},..,m^{\prime}_4\}})
\\
\texttt{Consistancy} =\;& \texttt{EdgeC} \land
\texttt{ActivityC} \land \texttt{PairingC} \land
\texttt{Fusion1} \land \texttt{Fusion2} 
\end{align*}
\texttt{EdgeC} states that each edge has at least one molecule,
there are no self loops, and edge labels are consistent with node labels.   
\texttt{ActivityC} states that active molecule are present.
\texttt{PairingC} states that all molecules are divided into two types
using $qr_m$ bit, which encodes if $m$ belongs to one type or another,
and any fusing set of molecules must have three molecules involved
from one type and one molecule from the other.
\texttt{Fusion1}, and \texttt{Fusion2} states the well-fused condition.
\texttt{Consistancy} is the conjunction of all of the above.

### 2019-03-19 papers/journal/experiments.tex
exmaple update

All the experiments were done
%Each test was run 
on a machine with Intel(R) Core(TM) i7-2600 CPU @ 3.40GHz processor and 16GB RAM.
%
A 120 min (7200 sec) timeout was used for the tool.

@@

%
Table~\ref{tab:satsmt-graph} presents the comparison of the running times of {\smttool} and {\sattool} on VTS variations of sizes 2 to 10.
%
For this comparison we have fixed the total number of molecules minimum twice the node count 
%for $ |N|> 2$ and $2|N| + 1$ for $|N| = 2$
%
%For each variant, we fix 1
and maximum number of parallel
edges to be 2.
%
%
In the table M/O indicates the search results in out of memory, T/O indicates a time out and ``!'' indicate that no model exists for the constraint  (constraints were unsatisfiable).
%In the table we have shown comparison for specific connectivity, for example variant A is checked against any graph with connectivity 2, variant B with connectivity 3 similarly for the rest of the variants.
%
%We have compared our performance with the performance of our earlier CBMC based implementation (old-encoding).
%
As an example, the result of verifying the formula for variation C of 2-connected, 10 compartment graph took 1977.72 secs for a satisfying result.
%
In comparison, {\sattool} was unable to solve the instance and ran out of memory.
% for $|N|$ greater than 5.
%
% 
The recursive encoding also performed better for the cases where the instance was unsatisfiable (Variant A timing comparison).
%instead of enumeration, not only we got efficiency improved for finding a SAT model but also did better in the case of refutation that no model exist (table~\ref{tab:satsmt-graph} Variant A timing comparison and Variant D with N =2). 
%
Hence with the use of improved encoding of reachability, we were able to scale the system to the biologically relevant compartment size, the
%a much larger compartmentalized system, especially to interesting 
the case of eukaryotic cells with a total number of 10 compartments.
%
Furthermore, we experimented with limits of our tools and found that {\smttool} was able to solve the constraints up to $18$ nodes.

@@

We have applied~\ourtool~on six partially defined VTSs.
%
The results are presented in Fig~\ref{tab:synth-graph} for both the solvers
\depqbf and \zthree.
%
To use~\zthree, we remove \texttt{Connected} constraints, such that the queries becomes
quantifier-free.
%
% The experiments were conducted on a machine,
% with \ashu{?}MHz processor, \ashu{?}GB memory, and 900s timeout.
%
%The experiments were conducted with a 900s timeout.
%
The first four VTSs are synthetic but inspire from literature for
typical motifs in VTSs. 
The third VTS is a subgraph of the last VTS.
%
%
The fifth VTS is taken from~\cite{burri2004complete}.
%
The last VTS represent mammalian SNARE map created by studying the literature references.  
%
The fig shows timing for various synthesis queries.
%
For each synthesis query, we have two columns.
%
One column reports the timing and the other reports the minimum changes needed to obtain a valid VTS.
%
$\infty$ indicates that any number of changes with the synthesis query
search space can obtain the VTS.
%
%\ashu{@ankit: please discuss all the synthesis queries in the table.}

>>>>

All the experiments were done
%Each test was run 
on a machine with Intel(R) Core(TM) i7-2600 CPU @ 3.40GHz processor and 16GB RAM.
%
A 45 min (2700 sec) timeout was used for the tool.

@@

%
Table~\ref{tab:satsmt-graph} presents the comparison of the running times of {\smttool} and {\sattool} on VTS variations of sizes 2 to 10.
%
For this comparison we have fixed the total number of molecules minimum four times the node count 
%for $ |N|> 2$ and $2|N| + 1$ for $|N| = 2$
%
%For each variant, we fix 1
and maximum number of parallel
edges to be 2.
%
For our analysis we relax the 3:1 requirement for the Q and R-SNARES and treat a Q-SNARE triple helix as a single complex as modelled in~\cite{shukla2017discovering}.
%
The 
%
In the table M/O indicates the search results in out of memory, T/O indicates a time out and ``!'' indicate that no model exists for the constraint  (constraints were unsatisfiable).
%In the table we have shown comparison for specific connectivity, for example variant A is checked against any graph with connectivity 2, variant B with connectivity 3 similarly for the rest of the variants.
%
%We have compared our performance with the performance of our earlier CBMC based implementation (old-encoding).
%
As an example, the result of verifying the formula for variation C of 2-connected, 10 compartment graph took 1977.72 secs for a satisfying result.
%
In comparison, {\sattool} was unable to solve the instance and ran out of memory.
% for $|N|$ greater than 5.
%
% 
The recursive encoding also performed better for the cases where the instance was unsatisfiable (Variant A timing comparison).
%instead of enumeration, not only we got efficiency improved for finding a SAT model but also did better in the case of refutation that no model exist (table~\ref{tab:satsmt-graph} Variant A timing comparison and Variant D with N =2). 
%
Hence with the use of improved encoding of reachability, we were able to scale the system to the biologically relevant compartment size, the
%a much larger compartmentalized system, especially to interesting 
the case of eukaryotic cells with a total number of 10 compartments.
%
Furthermore, we experimented with limits of our tools and found that {\smttool} was able to solve the constraints up to $18$ nodes.

@@

We have applied~\ourtool~on seven partially defined VTSs.
%
The results are presented in Fig~\ref{tab:synth-graph} for both the solvers
\depqbf and \zthree.
%
To use~\zthree, we remove \texttt{Connected} constraints, such that the queries becomes
quantifier-free.
%
% The experiments were conducted on a machine,
% with \ashu{?}MHz processor, \ashu{?}GB memory, and 900s timeout.
%
%The experiments were conducted with a 900s timeout.
%
The first four and the sixth VTSs are synthetic but inspire from literature for
typical motifs in VTSs. 
%
The third VTS is a subgraph of the last VTS.
%
%
The fifth VTS is taken from~\cite{burri2004complete}.
%
The last VTS represent mammalian SNARE map created by studying the literature references.  
%
The fig shows timing for various synthesis queries.
%
For each synthesis query, we have two columns.
%
One column reports the timing and the other reports the minimum changes needed to obtain a valid VTS.
%
$\infty$ indicates that any number of changes with the synthesis query
search space can obtain the VTS.
%
%\ashu{@ankit: please discuss all the synthesis queries in the table.}

### 2019-03-19 papers/journal/synth-table.tex
exmaple update

		plos1-dia[3C]& 0.012 &$\infty$& 0.312 &$\infty$& 0.669 & $\infty$ & 0.966 &$\infty$& 0.277 & -1 E, -1 AE, -1 AN. +1 E, +1 N. \\\hline
		plos2-dia[4C] & 0.014 & 0   & 0.322 & 0  & 1.409  & 0 & 2.114 & 0 &  0.337 & 0 \\\hline
		sub-mammal[3C]  & 0.767 & 1 E  & 1.049 & 5 PE & 3.523 & 1E & 4.961 & 1E & 1.172  & -1 E, -2 PE, -1 AN. +1 E, +4 PE, +4 N, +2 AN, +2 AE. \\\hline
		node4[3C]  & 1.554  & 1 E   &  3.859 & 12 PE  &  5.286  & $\infty$ & 4.502 &$\infty$& 2.194  & -2 E, -2 PE, -1 N, -1 AN, -1 AE. +12 N, +8 E, +1 PE.\\\hline
		%   yeast-graph[3C]   & 95.016    & 1 E   & 94.520   & 1 E   & 169.430  & 1 E & 172.35   & 1E   & 107.43  &  -1 E, -2 N, -2 AE, -2 AN. +2 E, 12 PE, 7 N. \\\hline
		yeast-graph[3C]   & 95.016    & 2 E  &   timeout  & N/A   & 1571.42  & 2 E  & 530.210   & 2 E & 72.316  &  -1 E, -1 N, -1 AE, -1 AN, -1PE. +2 E, 7 PE, 8 N. \\\hline

		mammal-graph[3C]  &  timeout     & N/A  &  timeout     & N/A    &  timeout         & N/A      &  timeout    &  N/A    &  timeout     & N/A\\\hline
		%    & 0.0    & 0.0    & 0.0    & 0.0    & 0.0         & 0.0      & 0.0   & 0.0    & 0.0    & 0.0\\\hline
	\end{tabular}
	% \caption{Run-times for searching for models (in secs). \#C  stands for minimum changes.
	% Time is reported in seconds.}
	% \label{tab:qf-graph}
	% \end{table}
	\begin{tabular}[t]{|c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}C{4cm}@{}|}\hline
		{\multirow{2}{*} \textbf{}}  & \multicolumn{2}{c|}{\textbf{Add}} & \multicolumn{2}{c|}{\textbf{Add}} & \multicolumn{2}{c|}{\textbf{Learning NNF}}  &  \multicolumn{2}{c|}{\textbf{Learning}} &  \multicolumn{2}{c|}{\textbf{Add/Delete}} \\
		{\multirow{2}{*} \textbf{Table b}}  & \multicolumn{2}{c|}{\textbf{edge}} & \multicolumn{2}{c|}{\textbf{molecules}} & \multicolumn{2}{c|}{\textbf{(only $\land$ and $\lor$)}}  &  \multicolumn{2}{c|}{\textbf{k-CNF}} &  \multicolumn{2}{c|}{\textbf{parts}} \\
		\cline{2-11}
		{} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} \\
		\hline

		plos1-dia & 0.041&$\infty$& 0.320 &$\infty$& 0.225 & $\infty$ & 0.33&$\infty$& 3.74 & -1 E, -1 PE, - 1 N, -1 PE. +1 AE, +1 PE, +1 N\\\hline
		plos2-dia & 3.97 & 0 &  2.647 & 0  & 5.941 & 0 & 5.680 & 0 & 3.56 & 0 \\\hline
		sub-mammal & 3.483 & 1 E  & 4.379 & 5 PE  & 29.980 & 1 E  & 10.405 & 1 E & 3.650  & -1 E, -2 PE, -1 AN. +1 E, +4 PE, +4 N, +2 AN, +2 AE \\\hline
		node4  & 4.150  & 1 E  & 10.562  & 12 PE & 3.401  & $\infty$ & 4.760 &$\infty$&  5.05  & -2 E, -2 PE, -1 N, -1 AN, -1 AE. +12 N, +8 E, +1 PE \\\hline
		yeast-graph & 40.225  & 2 E  &   timeout  & N/A   & 1393.84  & 2 E  & 468.161   & 2 E & 69.81  &  -1 E, -1 N, -1 AE, -1 AN, -1PE. +2 E, 7 PE, 8 N. \\\hline
		mammal-graph   &  timeout     & N/A  &  timeout     & N/A    &  timeout         & N/A      &  timeout    &  N/A   &  timeout     & N/A\\\hline
	\end{tabular}
	\caption{Run-times for synthesis queries. \#C stands for minimum changes in the synthesized VTS in comparison with the given partial VTS. Time is reported in seconds. (a) The solver used is DepQBF (b) The solver used is Z3. The sub-mammal is a subgraph of the complete mammal-graph. In the Add/Delete parts column, ‘+’n sign is used to show the addition of n number of the molecules, similarly ‘-’n is used to show the removal of n number of molecules. In the table, N is node labels, AN is active node molecules, E is edges, PE is molecule presence on the edge and AE is active molecules on the edge. The [kC] stands for k graph connectedness which is part of only DepQBF experiments.}

>>>>

		plos1-dia[3C]& 0.02 &$\infty$& 0.37 &$\infty$& 0.46 & $\infty$ & 0.63 &$\infty$& 0.21 & -1 E, -1AE, -1AN. +1E, +1N. \\\hline
		plos2-dia[4C] & 2.02 & 0   & 2.38 & 0  & 4.27  & 0 & 5.94 & 0 &  3.30 & 0 \\\hline
		sub-mammal[3C]  & 4.61 & 1 E  & 5.98 & 5 PE & 27.33 & 1 E & 14.75 & 1 E & 6.82  & -1E, -2PE, -1AN. +1E, +4PE, +4N, +2AN, +2AE. \\\hline
		node4[3C]  & 5.93  & 1 E   &  13.72 & 12 PE  &  5.09  & $\infty$ & 4.30 &$\infty$& 7.21  & -2 E, -2PE, -1 N, -1AN, -1 AE. +12 N, +8E, +1PE.\\\hline
		%   yeast-graph[3C]   & 95.016    & 1 E   & 94.520   & 1 E   & 169.430  & 1 E & 172.35   & 1E   & 107.43  &  -1 E, -2 N, -2 AE, -2 AN. +2 E, 12 PE, 7 N. \\\hline
		yeast-graph[3C]   & 105.15    & 2 E  &   247.04  & 15 PE   & 1381.24  & 2 E  & 541.66   & 2 E & 326.09  &  -1E, -1N, -1AE, -1AN, -1PE. +2E, +11PE, +20N. \\\hline
	   	node6[3C]  &  454.98  & 2 E  &  1209.30    & 21 PE    &  T/O  & N/A      &  T/O   &  N/A   &  T/O     & N/A \\\hline
		mammal-graph[3C]  &  T/O     & N/A  &  T/O     & N/A    &  T/O         & N/A      &  T/O    &  N/A    &  T/O     & N/A\\\hline
		%    & 0.0    & 0.0    & 0.0    & 0.0    & 0.0         & 0.0      & 0.0   & 0.0    & 0.0    & 0.0\\\hline
	\end{tabular}
	% \caption{Run-times for searching for models (in secs). \#C  stands for minimum changes.
	% Time is reported in seconds.}
	% \label{tab:qf-graph}
	% \end{table}
	\begin{tabular}[t]{|c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}c@{}|@{}C{4cm}@{}|}\hline
		{\multirow{2}{*} \textbf{}}  & \multicolumn{2}{c|}{\textbf{Add}} & \multicolumn{2}{c|}{\textbf{Add}} & \multicolumn{2}{c|}{\textbf{Learning NNF}}  &  \multicolumn{2}{c|}{\textbf{Learning}} &  \multicolumn{2}{c|}{\textbf{Add/Delete}} \\
		{\multirow{2}{*} \textbf{Table b}}  & \multicolumn{2}{c|}{\textbf{edge}} & \multicolumn{2}{c|}{\textbf{molecules}} & \multicolumn{2}{c|}{\textbf{(only $\land$ and $\lor$)}}  &  \multicolumn{2}{c|}{\textbf{k-CNF}} &  \multicolumn{2}{c|}{\textbf{parts}} \\
		\cline{2-11}
		{} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} & {\textbf{Time}} & {\textbf{\#C}} \\
		\hline

		plos1-dia & 0.04&$\infty$& 0.31 &$\infty$& 0.20 & $\infty$ & 0.27&$\infty$& 3.47 & -1E, -1PE, - 1N, -1PE. +1AE, +1PE, +1N\\\hline
		plos2-dia & 3.97 & 0 &  2.26 & 0  & 5.46 & 0 & 5.35 & 0 & 3.24 & 0 \\\hline
		sub-mammal & 3.22 & 1 E  & 4.18 & 5 PE  & 24.73 & 1 E  & 9.21 & 1 E & 5.36  & -1E, -2PE, -1AN. +1 E, +4PE, +4N, +2AN, +2AE \\\hline
		node4  & 4.01  & 1 E  & 10.19  & 12 PE & 4.26  & $\infty$ & 4.13 &$\infty$&  6.89  & -2 E, -2PE, -1N, -1AN, -1AE. +12N, +8E, +1PE \\\hline
		yeast-graph & 38.68  & 2 E  &   127.45  & 15 PE   & 1002.41  & 2 E  & 434.08   & 2 E & 197.82  &  -1E, -1N, -1AE, -1AN, -1PE. +2E, +11PE, +20N. \\\hline
		node6  &  235.97  & 2 E  &  549.25    & 21 PE    &  T/O  & N/A      &  T/O   &  N/A   &  T/O     & N/A \\\hline
		mammal-graph   &  T/O     & N/A  &  T/O    & N/A    &  T/O  & N/A      &  T/O   &  N/A   &  T/O     & N/A\\\hline
	\end{tabular}
	\caption{Run-times for synthesis queries. \#C stands for minimum changes in the synthesized VTS in comparison with the given partial VTS. Time is reported in seconds. (a) The solver used is DepQBF (b) The solver used is Z3. The sub-mammal is a subgraph of the complete mammal-graph. In the Add/Delete parts column, ‘+’n sign is used to show the addition of n number of the molecules, similarly ‘-’n is used to show the removal of n number of molecules. In the table, N is node labels, AN is active node molecules, E is edges, PE is molecule presence on the edge and AE is active molecules on the edge. The [kC] stands for k graph connectedness which is part of only DepQBF experiments.}
